\section*{The Essential Parity Traversal}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Time Limit:} & 1.0 second \\
\textbf{Memory Limit:} & 256 megabytes \\
\hline
\end{tabular}
\end{center}

\subsection*{Problem Description}

You are given a directed graph $G=(V, E)$ consisting of $N$ vertices and $M$ edges. Each edge $e \in E$ has a non-negative integer weight $w(e) \ge 0$. The vertices are 1-indexed.

A specific set of $K$ vertices, denoted $V_{ess}$, is designated as 'Essential Nodes'. You are given a source vertex $S$ and a target vertex $T$. Both $S$ and $T$ are guaranteed to be essential nodes, $S, T \in V_{ess}$.

Your task is to find a path $P$ from $S$ to $T$ such that its total weight, denoted $W(P)$, is minimized, subject to two strict requirements:

\begin{enumerate}
    \item \textbf{Simplicity:} The path $P$ must be a simple path. That is, $P$ must visit no vertex more than once.
    \item \textbf{Parity:} The length of the path, $L(P)$ (defined as the number of edges in $P$), must be odd.
\end{enumerate}

Determine the minimum total weight $W(P)$ satisfying both conditions.

\subsection*{Input Format}

The first line contains five integers: $N$, $M$, $K$, $S$, and $T$ ($1 \le N \le 50,000$; $1 \le M \le 100,000$; $2 \le K \le 18$; $1 \le S, T \le N$, $S \neq T$). $N$ is the number of vertices, $M$ is the number of edges, $K$ is the number of essential nodes, $S$ is the source index, and $T$ is the target index.

The next $K$ lines each contain a single integer, listing the index of an essential node in $V_{ess}$. Note that $S$ and $T$ are guaranteed to be included in this list.

The next $M$ lines describe the edges. Each line contains three integers $u_i$, $v_i$, and $w_i$ ($1 \le u_i, v_i \le N$; $0 \le w_i \le 10^9$), indicating a directed edge from $u_i$ to $v_i$ with weight $w_i$.

\subsection*{Output Format}

Output a single integer representing the minimum weight of an odd-length simple path from $S$ to $T$. If no such path exists, output \texttt{-1}.

\subsection*{Constraints}

\begin{itemize}
    \item $1 \le N \le 50,000$
    \item $1 \le M \le 100,000$
    \item $2 \le K \le 18$
    \item $0 \le w_i \le 10^9$
    \item $S$ and $T$ are distinct essential nodes.
\end{itemize}

\subsection*{Sample Input}
\begin{verbatim}
5 6 3 1 5
1
3
5
1 2 1
2 3 1
3 5 1
1 4 10
4 2 1
2 5 1
\end{verbatim}

\subsection*{Sample Output}
\begin{verbatim}
3
\end{verbatim}

\subsubsection*{Explanation for Sample}

The graph has $N=5$ vertices. Source $S=1$, Target $T=5$. Essential nodes are $\{1, 3, 5\}$.

We seek a minimum weight path with an odd number of edges.

\begin{itemize}
    \item Path $P_1$: $1 \to 2 \to 5$. Length $L=2$ (Even). Weight $1 + 1 = 2$. (Invalid length)
    \item Path $P_2$: $1 \to 2 \to 3 \to 5$. Length $L=3$ (Odd). Weight $1 + 1 + 1 = 3$. This path is simple.
    \item Path $P_3$: $1 \to 4 \to 2 \to 5$. Length $L=3$ (Odd). Weight $10 + 1 + 1 = 12$. This path is simple.
\end{itemize}
The minimum weight for a path satisfying the odd length and simplicity requirements is 3.