\documentclass{article}
\usepackage{amsmath, amssymb, fullpage}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\setlength{\parindent}{0pt}

\begin{document}

\section*{Problem Description}

In the heart of the Quantum Lattice, $n$ entangled qubit resonators form the foundation of reality stabilization. Each resonator $i$ can exist in a \textit{ground state} ($0$) or an \textit{excited state} ($1$). The Lattice is protected by $m$ Chrono-Parity Safeguards—ancient protocols established by the Cosmic Weavers to prevent quantum decoherence.

Each safeguard is defined by a tuple $(t, l, r, j)$:
\begin{itemize}
    \item \textbf{Type A} ($t = 0$): If the segment $[l, r]$ contains an \textit{even} number of resonators, then for every resonator $i \in [l, r]$, if $i$ is in ground state, resonator $j$ \textit{must} be excited.
    \item \textbf{Type B} ($t = 1$): If the segment $[l, r]$ contains an \textit{odd} number of resonators, then for every resonator $i \in [l, r]$, if $j$ is excited, resonator $i$ \textit{must} be in ground state.
\end{itemize}

Your mission is to determine whether a valid state configuration exists that satisfies \textbf{all} active Chrono-Parity Safeguards. Note that a safeguard is only active when its parity condition holds; otherwise, it imposes no constraints.

Formally, given integers $n$ and $m$, and $m$ quadruples $(t, l, r, j)$, decide if there exists a binary array $s[1..n]$ such that for every quadruple:
\begin{itemize}
    \item If $t = 0$ and $(r - l + 1) \equiv 0 \pmod{2}$, then $\forall i \in [l, r]$, $s[i] = 0 \implies s[j] = 1$.
    \item If $t = 1$ and $(r - l + 1) \equiv 1 \pmod{2}$, then $\forall i \in [l, r]$, $s[j] = 1 \implies s[i] = 0$.
\end{itemize}

This problem lies at the intersection of constraint satisfaction and combinatorial parity logic, requiring deep structural insight to resolve within stringent computational limits.

\section*{Input}

The first line contains two integers $n$ and $m$ ($1 \leq n, m \leq 10^5$).

Each of the next $m$ lines contains four integers $t$, $l$, $r$, $j$ ($t \in \{0, 1\}$, $1 \leq l \leq r \leq n$, $1 \leq j \leq n$), describing a Chrono-Parity Safeguard.

\section*{Output}

Print \texttt{YES} if a valid state assignment exists, otherwise print \texttt{NO}.

\section*{Constraints}

\begin{itemize}
    \item $1 \leq n, m \leq 10^5$
    \item $1 \leq l \leq r \leq n$
    \item $1 \leq j \leq n$
    \item $t \in \{0, 1\}$ for all safeguards
\end{itemize}

\section*{Sample}

\textbf{Sample Input:}
\begin{verbatim}
2 2
0 1 2 1
0 1 2 2
\end{verbatim}

\textbf{Sample Output:}
\begin{verbatim}
YES
\end{verbatim}

\textbf{Sample Input:}
\begin{verbatim}
2 3
0 1 2 1
0 1 2 2
1 1 1 2
\end{verbatim}

\textbf{Sample Output:}
\begin{verbatim}
NO
\end{verbatim}

\end{document}