\documentclass{article}
\usepackage{amsmath, amssymb, fullpage}

\begin{document}

\section*{Problem Description}
In the year 2147, quantum signal processors have revolutionized communication across the galaxy. These processors interpret cosmic background radiation as digit strings, where specific substrings called ``resonant echoes'' indicate stable wormhole formations. A resonant echo is defined as a substring whose numeric value is divisible by $2^L$, where $L$ is the length of the substring. Dr. Elara Vance, lead scientist at the Nebula Research Institute, needs your expertise to count these echoes in real-time to prevent catastrophic signal interference. The challenge: process signals of up to $10^5$ digits efficiently, as brute-force methods would collapse the quantum state.

Formally, given a string $S$ of $n$ digits, count the number of contiguous substrings $S[i..j]$ ($1 \leq i \leq j \leq n$) such that the integer formed by $S[i..j]$ is divisible by $2^{j-i+1}$.

\section*{Input}
The first line contains an integer $n$ ($1 \leq n \leq 10^5$), the length of the quantum signal string. The second line contains a string $S$ of exactly $n$ digits (each character is between '0' and '9', inclusive).

\section*{Output}
Output a single integer: the number of resonant echoes in $S$.

\section*{Constraints}
\begin{itemize}
    \item $1 \leq n \leq 10^5$
    \item $S$ consists only of digits '0'--'9'
\end{itemize}

\section*{Sample}
\textbf{Input:}
\begin{verbatim}
4
1234
\end{verbatim}

\textbf{Output:}
\begin{verbatim}
3
\end{verbatim}

\end{document}